Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-08-08 paper/paper.tex
Maybe we want reproduction plots
Write more, pretend it's progress

\section{Experiments with Parallel Search}

?? Hardware.

?? Datasets.

@@

@@

>>>>

\section{Parallel Search}

?? Approach

\section{Empirical Evaluation}

We perform our experiments on systems with dual Intel Xeon E5-2640 v2 processors and 64GBytes RAM,
running Ubuntu 14.04, with GCC 5.3.0 as the compiler. Each machine has a total of sixteen cores, and
hyper-threading is enabled, so we run experiments with 32 threads except where otherwise noted.
Most of our instances come from a standard benchmark set
\citep{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07} for maximum common subgraph
problems.  This benchmark set can be used in a number of ways, for different variants of the
problem. We use it to create five families of instance, as follows:

\begin{description}
    \item[Unlabelled] instances, by selecting the first ten members of each parameter class where the
        graphs have up to 50 vertices each---this gives us a total of 4,110 instances.

    \item[Vertex labelled] instances, by selecting the first ten members of each parameter class
        (and so graphs have up to 100 vertices each), applying the 33\% labelling scheme for
        vertices only, and treating edges as undirected. This gives 8,140 instances.

    \item[Both labelled, directed] instances, by selecting the first ten members of each parameter
        class, and applying the 33\% labelling scheme to both vertices and edges. Again, this gives
        8,140 instances.

    \item[Unlabelled, connected] instances, using the same instances as the \emph{unlabelled} case.

    \item[Both labelled, connected] instances, starting in the same way as the \emph{both labelled,
        directed} case. These are then converted to undirected graphs by treating edges as
        undirected, picking the label of the lower-numbered edge.
\end{description}

\noindent
Following \citet{DBLP:conf/aaai/HoffmannMR17}, we also work with the 5,725 \textbf{Large} instances
originally used for studying portfolios of subgraph isomorphism algorithms
\citep{DBLP:conf/lion/KotthoffMS16}. These graphs are unlabelled and undirected, and can include up
to 6,671 vertices. We do not use the clique encoding on these instances due to its impractical
memory requirements for large graphs.

@@

\begin{figure}[tb]
    \includegraphics*{gen-graph-scatter-plain-kdown-par-t4-vs-kdown-par-t16.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-kdown-par-t32r-vs-kdown-par-t32.pdf}

    \caption{Scalability and reproducibility of the $k{\downarrow}$ algorithm.}
\end{figure}

@@

\begin{figure}[tb]
    \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t4-vs-mcsplit-par-t16.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t32r-vs-mcsplit-par-t32.pdf}

    \caption{Scalability and reproducibility of the splitting algorithm.}
\end{figure}
